MSAD_PCA_Walkthrough

### 2017-10-18 README.Rmd
On my mac, I used devtools::build() to create the .tar.gz file for CRAN submission. After a few hours of reading, I settled on the GPLv2 license: it does not conflict with university IP regulations, it's supported by OSI, recognised by the NSF, and seems to offer adequate protection.
I also used the --as-cran option for devtools::check() and still passed with 0-0-0. The last push passed with 0-0-0 on Travis as well.

## Overview
We create this package, `mvMonitoring`, from the foundation laid by Kazor et al (2016). The `mvMonitor` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.

@@

>>>>

## Overview
We create this package, `mvMonitoring`, from the foundation laid by Kazor et al (2016). This package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.

@@

## Acknowledgements
This work is  supported by the King Abdullah University of Science and Technology (KAUST) Office of Sponsored Research (OSR) under Award No: OSR-2015-CRG4-2582 and by the National Science Foundation PFI:BIC Award No: 1632227.
